---
title: "Bar_charts"
output: html_document
date: "2024-02-17"
---
```{r}
library(ggplot2)
library(tidyverse)
```

```{r}
mpg[1:10,c(1,2,3,7,9,10,11)]
```

## For geom_bar(), the default behavior is to count the rows for each x value. It doesn't expect a y-value, since it's going to count that up itself.

```{r}
ggplot(mpg, aes(class))+ geom_bar()
# Equal to ggplot(mpg, aes(class))+ geom_bar(stat = "count")
```

## For geom_col, it expects you to already have the y values calculated and to use them directly.
```{r}
mpg_count=mpg %>% group_by(class) %>% summarise(count_n=n()) %>% ungroup()
mpg_count
```

```{r}
ggplot(mpg_count, aes(class,count_n))+ geom_col()
```
## You can also use geom_bar(stat = "identity"), then it is the same as geom_col()

```{r}
ggplot(mpg_count, aes(class,count_n))+ geom_bar(stat = "identity")+
  geom_text(aes(label=count_n), vjust=-0.3, size=3.5)
```

## If there are subtypes within each group, we can either stack them or put them side-by-side
```{r}
mpg_drv_count=mpg %>% group_by(class, drv) %>% summarise(count_n=n()) %>% ungroup()
mpg_drv_count
```

```{r}
ggplot(mpg_drv_count, aes(class,count_n))+ geom_col()
```

```{r}
ggplot(mpg_drv_count, aes(class,count_n,fill=drv))+ geom_col()
# default geom_col(position = "stack")
```

```{r}
ggplot(mpg_drv_count, aes(class,count_n,fill=drv))+ geom_col(position = "dodge")
```

