---
title: "Boxplot"
output: html_document
date: "2024-02-18"
---

```{r}
library(ggplot2)
library(tibble)
library(patchwork)
library(ggpubr)
```

```{r}
InsectSprays[1:15,]
```

```{r}
ggplot(aes(y = count, x = spray, fill=spray), data = InsectSprays) +
  geom_boxplot(outlier.shape = 4)+
  theme_bw()
```

## Add the raw data point, you may want to turn off outlier for boxplot to prevent the same outlier from showing twice
```{r}
ggplot(aes(y = count, x = spray, fill=spray), data = InsectSprays) +
  geom_boxplot(outlier.shape  = NA)+
  geom_jitter(color="black", size=0.4, alpha=0.9, width = 0.2) +
  theme_bw()
```

## Plot with ggpubr
```{r}
ggboxplot(InsectSprays, x = "spray", y = "count",
                color = "spray",add = "jitter")
```

## Plot paired data with ggpubr
```{r}
# Chick is an ordered factor with levels 18 < … < 48 giving a unique identifier for the chick. 
head(ChickWeight[ChickWeight$Diet==1,])
```


```{r}
ggpaired(ChickWeight[ChickWeight$Diet==1,], x = "Time", y = "weight",id = "Chick",
 color = "Time", line.color = "gray", line.size = 0.4,xlab = "Time", ylab = "weight")
```

## Notched box plot
### In a notched box plot, the notches extend 1.58 * IQR / sqrt(n), (where IQR is the inter-quartile range, or distance between the first and third quartiles). This gives a roughly 95% confidence interval for comparing medians.
### If the notches (confidence interval) of two groups do not overlap, that indicates they are significantly different.
### However, if the confidence interval is larger than IQR, the figure will look weird.

```{r}
x <- rnorm(150)
y <- rnorm(50, mean=0.8)

g1=ggplot(
  data = data.frame(
    num = c(x, y),
    idx = c(rep("x", 150), rep("y", 50))
  ),
  aes(x = idx, y = num, fill = idx)
) +
  geom_boxplot(notch = TRUE)

g2=ggplot(aes(y = count, x = spray, fill=spray), data = InsectSprays) +
  geom_boxplot(notch = T, outlier.shape = 4, show.legend = F)+
  theme_bw()

g1+g2
```

## Violin plot
### Similar to box plots, except that they also show the kernel probability density of the data
```{r}
ggplot(aes(y = count, x = spray, fill=spray), data = InsectSprays) +
  geom_violin()+
  theme_bw()
```

## Violin plot with dots
```{r}
g1=ggplot(aes(y = count, x = spray), data = InsectSprays) +
  geom_violin(aes(fill=spray))+
  geom_dotplot(binaxis='y', stackdir='center',dotsize = 0.2)+
  theme_bw()

g2=ggplot(aes(y = count, x = spray, fill=spray), data = InsectSprays) +
  geom_violin()+
  geom_jitter(shape=16, position=position_jitter(0.2))+
  theme_bw()
g1+g2
```