---
title: "Heatmap"
output: html_document
date: "2024-02-25"
---

```{r}
library(RColorBrewer)
library(gplots)
```

```{r}
mtcars[1:5,]
```
```{r}
class(mtcars)
```

# A heat map is a false color image with a dendrogram added to the left side and/or to the top. Typically, the rows and columns are reordered according to the dendrogram.
```{r}
heatmap.2(as.matrix(mtcars), col = brewer.pal(9, "RdYlBu"), 
        scale = "none",trace = "none", density.info = "none", margins = c(4, 12))
```

## All the hp and disp variables that have very high values compared to the others. We need to normalize the data.
```{r}
heatmap.2(as.matrix(mtcars), col = brewer.pal(9, "RdYlBu"), 
        scale = "column",trace = "none", density.info = "none", margins = c(4, 12))
```

## By default, the heatmap is made using Euclidean distance, you can change it by setting up "distfun", or perform the hierarchical clustering first and draw heatmap according to the result.
```{r}
## Row clustering (adjust here distance/linkage methods to what you need!)
hr <- hclust(as.dist(1-cor(t(mtcars), method="pearson")), method="complete")
 
## Column clustering (adjust here distance/linkage methods to what you need!)
hc <- hclust(as.dist(1-cor(mtcars, method="spearman")), method="complete")
 
## Plot heatmap
heatmap.2(as.matrix(mtcars), Rowv=as.dendrogram(hr), Colv=as.dendrogram(hc), col = brewer.pal(9, "RdYlBu"),
          scale="column", density.info="none", trace="none", margins = c(4, 12))

```




