---
title: "Bar_charts"
output:
  html_document: default
  pdf_document: default
date: "2024-02-17"
---
```{r}
library(ggplot2)
library(patchwork)
```

```{r}
set.seed(3)
x1 <- rnorm(100, mean=1)
x2 <- rnorm(100, mean = 3)
x <- c(x1, x2)
group <- c(rep("G1", 100), rep("G2", 100))

df <- data.frame(x, group_G1_G2 = group)
df
```

## By default, if the histograms overlap, the values will be stacked. 

```{r}
ggplot(df, aes(x = x, fill = group_G1_G2, colour= group_G1_G2)) + 
  geom_histogram(alpha = 0.5)
```

## Seperate the stacked groups

```{r}
ggplot(df, aes(x = x, fill = group_G1_G2, colour= group_G1_G2)) + 
  geom_histogram(alpha = 0.5, position = "identity")
```

## Add an space between each bar so you will be able to see both histograms for different groups

```{r}
ggplot(df, aes(x = x, fill = group_G1_G2, colour= group_G1_G2)) + 
  geom_histogram(alpha = 0.5,position = "dodge")
```

## Change the number of bins

```{r}
g1=ggplot(df, aes(x = x, fill = group_G1_G2, colour= group_G1_G2)) + 
  geom_histogram(breaks = seq(-2, 6, by = 2), alpha = 0.5, position = "identity")

g2=ggplot(df, aes(x = x, fill = group_G1_G2, colour= group_G1_G2)) + 
  geom_histogram(bins = 3, alpha = 0.5, position = "identity")

g1+g2
```


## Custom legend fill colours

```{r}
g1=ggplot(df, aes(x = x, fill = group_G1_G2)) + 
  geom_histogram(alpha = 0.5, colour= 1, position = "identity")+
  scale_fill_manual(values = c("#8795E8", "#FF6AD5"))

g2=ggplot(df, aes(x = x, fill = group_G1_G2)) + 
  geom_histogram(alpha = 0.5, colour= 1, position = "identity")+
  scale_fill_brewer(palette ="Set1")

g1+g2
```

## Show densitiy instead of count
```{r}
g1=ggplot(df, aes(x = x, fill = group_G1_G2)) + 
  geom_histogram(alpha = 0.5, colour= 1, position = "identity")+ 
  theme(legend.position = "none")

g2=ggplot(df, aes(x = x, fill = group_G1_G2)) + 
  geom_histogram(aes(y = after_stat(density)), alpha = 0.5, colour= 1, position = "identity")+ 
  theme(legend.position = "none")
g1+g2
```

## Show density, a smoothed version of the histogram. For continuous data that comes from an underlying smooth distribution.
```{r}
ggplot(df, aes(x = x, fill = group_G1_G2)) + 
  geom_density(alpha = 0.5, colour= 1)
```

## Custom legend title and labels
```{r}
ggplot(df, aes(x = x, fill = group_G1_G2)) + 
  geom_histogram(alpha = 0.5, colour= 1, position = "identity")+
  scale_fill_discrete(labels = c("A", "B"))+ 
  guides(fill = guide_legend(title = "Title"))
```
