---
title: "Scatter_dot_plot"
output: html_document
date: "2024-02-24"
---

```{r}
library(ggplot2)
library(tibble)
library(patchwork)
library(ggpubr)
```

```{r}
mtcars[1:5,]
mtcars$cyl=as.factor(mtcars$cyl)
mtcars$vs=as.factor(mtcars$vs)
```

# Scatter plots. These are useful for plotting multivariate data. They can help you determine potential relationships among scale variables. ## Both x and y axis are continous variables
```{r}
g1=ggplot(mtcars, aes(x=wt, y=mpg)) + geom_point()
g2=ggplot(mtcars, aes(x=wt, y=mpg, shape=cyl, color=cyl)) +
  geom_point()
g1+g2
```

## Add the regression line
```{r}
g1=ggplot(mtcars, aes(x=wt, y=mpg)) + 
  geom_point() +
  geom_smooth(method=lm)

g2=ggplot(mtcars, aes(x=wt, y=mpg, shape=cyl, color=cyl)) +
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
g1+g2
```

# Dotplot. Like histograms, these are useful for showing the distribution of a single scale variable. The x axis is categorical data.
## You can see from the right figure, the nearby dots are binned and put on the same y axis level, we can also see the overlapping dots better.
```{r}
p1=ggplot(mtcars, aes(x=cyl, y=mpg)) + geom_point()
p2=ggplot(mtcars, aes(x=cyl, y=mpg)) + geom_dotplot(binaxis='y', stackdir='center')
p1+p2
```
## Dot plot with multiple groups
```{r}
ggplot(mtcars, aes(x=cyl, y=mpg, fill=vs)) +
  geom_dotplot(binaxis='y', stackdir='center', 
               position=position_dodge(0.8))
```
